### 2012-03-29 doc/theses/mikula/implementation.tex
Master thesis: Corrections.
Master thesis: In progress.

\section{jInfer Process of Inference}
\begin{figure}
\label{FIG_jinfer_steps}
\caption{jInfer process of inference.}
\includegraphics[scale=0.9]{jinfer_steps.eps}
\end{figure}

@@

\section{jInfer Modules}
\todo[inline]{Labely obrazku dat pod.}
\begin{figure}
\label{FIG_jinfer_modules}
\caption{jInfer modules.}
\includegraphics[scale=0.8]{jinfer_modules.eps}
\end{figure}

@@

Actually, the blue modules shown in Figure \ref{FIG_jinfer_modules} are module abstractions with specified interface. Actual modules are then implementations complying the interface. Since we provide only one implementation of modules for the proposed solution, this is not very important for this work and we do not describe the principle in detail.

As in the previous section, newly added modules are those shown in yellow boxes. They are \textbf{XQuery Processor} and \textbf{XQuery Importer}. We also modified modules \textbf{Basic XSD Exporter} (an implementation of \textbf{Schema Generator} interface) and \textbf{Base} to extend their functionality.

\begin{itemize}
\item \textbf{Base} - This is module containing common classes used by other modules and defining interfaces. We added five packages to this module. Package \texttt{cz.cuni.mff.ksi.jinfer.base.objects.xquery.syntaxtree.nodes} implements the structure of syntax trees. Package \texttt{cz.cuni.mff.ksi.jinfer\-.base.interfaces.xquery} contains \texttt{Type} interface which is an interface for types used in the type analysis of syntax trees. Package \texttt{cz.cuni.mff.ksi\-.jinfer.base\-.objects.xquery.types} contains implementations of \texttt{Type} interface and type utility classes. Package \texttt{cz.cuni.mff.ksi.jinfer\-.base\-.objects.xquery.keys} provides representations of keys and foreign keys, and package \texttt{cz.cuni.mff.ksi\-.jinfer.base.objects.xsd} provides representation of XSD built-in atomic types.
\item \textbf{XQuery Importer} - This module represents \textbf{XQAnalyzer} step in Figure \ref{FIG_jinfer_steps}. It is responsible for creating syntax trees from input XQuery files (step 1).
\item \textbf{XQuery Processor} - The main module consisting of steps \textbf{XQuery Processor} and \textbf{Merger} in Figure \ref{FIG_jinfer_steps}. Package \texttt{cz.cuni.mff.ksi.jinfer\-.xqueryanalyzer} contains the main module class \texttt{XQueryAnalyzerImpl}. Other packages are \texttt{cz.cuni.mff.ksi.jinfer.xqueryanalyzer.-\\expressiontypesanalysis} implementing the static analysis of expression types (step 2), \texttt{cz.cuni.mff.ksi.jinfer.xqueryanalyzer.builtintype\-inference} implementing the inference of XSD built-in types (step 3), \texttt{cz\-.cuni.mff\-.ksi.jinfer\-.xqueryanalyzer.keydiscovery} and their subpackages implementing the key discovery (step 4), \texttt{cz.cuni.mff.ksi.jinfer\-.xqueryanalyzer.merger} implementing the merging with the grammar, and \texttt{cz.cuni.mff.ksi.jinfer.xqueryanalyzer.utils} containing various utilities.
\item \textbf{Basic XSD Exporter} - This is the module responsible for generating the resulting schema in XSD. It was modified to process the additional information assigned to the grammar in \textbf{XQuery Processor} module.
\end{itemize}

>>>>

\section{jInfer Process of Inference}
\begin{figure}
\includegraphics[scale=0.9]{jinfer_steps.eps}
\caption{jInfer process of inference.}
\label{FIG_jinfer_steps}
\end{figure}

@@

\section{jInfer Modules}
\begin{figure}
\includegraphics[scale=0.8]{jinfer_modules.eps}
\caption{jInfer modules.}
\label{FIG_jinfer_modules}
\end{figure}

@@

Actually, the blue modules shown in Figure \ref{FIG_jinfer_modules} are module abstractions with specified interface. Actual modules are then implementations complying the interface. Since we provide only one implementation of modules for the proposed solution, this is not very important for this work and we do not describe the principle in detail. We only note that \textbf{Basic XQuery Processor} module is an implementation of \textbf{Non-grammatical Input Processor} module abstraction.

As in the previous section, newly added modules are those shown in yellow boxes. They are \textbf{Basic XQuery Processor} and \textbf{XQuery Importer}. We also modified modules \textbf{Basic XSD Exporter} (an implementation of \textbf{Schema Generator} interface) and \textbf{Base} to extend their functionality.

\begin{itemize}
\item \textbf{Base} - This is module containing common classes used by other modules and defining interfaces. We added five packages to this module. Package \texttt{cz.cuni.mff.ksi.jinfer.base.objects.xquery.syntaxtree.nodes} implements the structure of syntax trees. Package \texttt{cz.cuni.mff.ksi.jinfer\-.base.interfaces.xquery} contains \texttt{Type} interface which is an interface for types used in the type analysis of syntax trees. Package \texttt{cz.cuni.mff.ksi\-.jinfer.base\-.objects.xquery.types} contains implementations of \texttt{Type} interface and type utility classes. Package \texttt{cz.cuni.mff.ksi.jinfer\-.base\-.objects.xquery.keys} provides representations of keys and foreign keys, and package \texttt{cz.cuni.mff.ksi\-.jinfer.base.objects.xsd} provides representation of XSD built-in atomic types.
\item \textbf{XQuery Importer} - This module represents \textbf{XQAnalyzer} step in Figure \ref{FIG_jinfer_steps}. It is responsible for creating syntax trees from input XQuery files (step 1).
\item \textbf{Basic XQuery Processor} - The main module consisting of steps \textbf{XQuery Processor} and \textbf{Merger} in Figure \ref{FIG_jinfer_steps}. Package \texttt{cz.cuni.mff.ksi.jinfer\-.basicxqueryprocessor} contains the main module class \texttt{NonGrammatical\-InputProcessorImpl}. Other packages are \texttt{cz.cuni.mff.ksi.jinfer.\-basicxqueryprocessor.expressiontypesanalysis} implementing the static analysis of expression types (step 2), \texttt{cz.cuni.mff.ksi.jinfer.basic-\\xqueryprocessor.builtintype\-inference} implementing the inference of XSD built-in types (step 3), \texttt{cz\-.cuni.mff\-.ksi.jinfer\-.basicxquery-\\processor.keydiscovery} and their subpackages implementing the key discovery (step 4), \texttt{cz.cuni.mff.ksi.jinfer.basicxqueryprocessor.merger} implementing the merging with the grammar, and \texttt{cz.cuni.mff.ksi.jinfer\-.basicxqueryprocessor.utils} containing various utilities.
\item \textbf{Basic XSD Exporter} - This is the module responsible for generating the resulting schema in XSD. It was modified to process the additional information assigned to the grammar in \textbf{Basic XQuery Processor} module.
\end{itemize}
